The relative roles of genetic, ecological and environmental factors in insular species radiations

### 2018-05-14 paper/draft.tex
add some comments for intro and MM from PubClub

\section{Introduction}
Islands are understood as suitable model systems for ecology and evolution due to their well definable characteristics like isolation (e.g. Losos \& Ricklefs 2009; Warren et al. 2015  Islands as model systems in ecology and evolution: prospects fifty years after MacArthur‐Wilson. EcoLett). %TODO: ref
Part of this value as study system originates by typically remarkable species. In fact, islands often possess unique species communities and can exceede mainland areas by a factor of 9.5 and 8.1 in plant and animal  endemism, respectively (Kier et al. 2005. A global assessment of endemism and species richness across island and mainland regions. PNAS). %TODO: refs
Such high endemism makes islands  especially threatened by human impacts, in particular climate change and invasive species (Fordham \& Brook 2010). %TODO: refs
Hence, understanding the origin, maintenance, functioning and evolution of island communities is of a high priority objective.

@@

\section{Material and Methods}
We use an individual-based metacommunity model written in julia %\cite{JULIALANG}.
Each individual is characterized by a set of genetically controlled (i.e. genomically-coded) traits, which influence ecological processes of
establishment, competition, growth, (density independent) mortality, reproduction and dispersal.
The simulation arena consists of a larger landmass (the mainland) holding an initial random species pool and a smaller, initially unpopulated island some distance apart (user-defined in the experimental design). % it would be nice to hav a table with all model configurations that can be defined by the user upon designing the experiment. This might help readers see that the model is general enough to be applied to any ecological arena (mainland-island being one).
During the course of the simulation, individuals may disperse from the mainland to the island, thus colonizing it. 
The complete state of the simulation is recorded every 1000 time steps for analysis.

>>>>

\section{Introduction}
%% Intro subsections (==paragraphs):
%% 1. Major topic (include only background relevant for exp. design)
%% 2. Islands
%% 3. Forces
%% 4. Models
%% 5. Aim, Objectives
%% 2+3 may be combined, as well as 1+2(+3)

Islands are understood as suitable model systems for ecology and evolution due to their well definable characteristics like isolation (e.g. Losos \& Ricklefs 2009; Warren et al. 2015  Islands as model systems in ecology and evolution: prospects fifty years after MacArthur‐Wilson. EcoLett). %TODO: ref
Part of this value as study system originates by typically remarkable species. In fact, islands often possess unique species communities and can exceede mainland areas by a factor of 9.5 and 8.1 in plant and animal  endemism, respectively (Kier et al. 2005. A global assessment of endemism and species richness across island and mainland regions. PNAS). %TODO: refs
Such high endemism makes islands  especially threatened by human impacts, in particular climate change and invasive species (Fordham \& Brook 2010). %TODO: refs
Hence, understanding the origin, maintenance, functioning and evolution of island communities is of a high priority objective.

@@

\section{Material and Methods}
%% Include simplified model description ``based on ODD''
%% scheduling (order of processes)
%% justify each decision with reference
%% Experimental design
We use an individual-based metacommunity model written in julia %\cite{JULIALANG}.
Each individual is characterized by a set of genetically controlled (i.e. genomically-coded) traits, which influence ecological processes of
establishment, competition, growth, (density independent) mortality, reproduction and dispersal.
The simulation arena consists of a larger landmass (the mainland) holding an initial random species pool and a smaller, initially unpopulated island some distance apart (user-defined in the experimental design). % it would be nice to hav a table with all model configurations that can be defined by the user upon designing the experiment. This might help readers see that the model is general enough to be applied to any ecological arena (mainland-island being one).
During the course of the simulation, individuals may disperse from the mainland to the island, thus colonizing it. 
The complete state of the simulation is recorded every 1000 time steps for analysis.
